Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
hscc17

The digital controllers synthesized in this paper are typically used in closed loops with continuous (and physical) plants. Thus, the proposed approach has to consider dynamics of continuous parts of system ({\it e.g.}, plant) and discrete parts ({\it e.g.}, digital controller), {\it i.e.} the synthesized controller has to consider the issues related to the hybrid systems studies.

@@

The vector of parametric coefficient uncertainties $\Delta{p}$ of $\Delta{G}_p(z)$ is defined by:
\begin{equation}
\Delta{\vec{p}}=\begin{bmatrix}
\hat{b_{0}} - b_{0}\\
\hat{b_{1}} - b_{1}\\
\vdots \\
\hat{b}_{M_G} - b_{M_{G}}\\
\hat{a_{0}} - a_{0}\\
\hat{a_{1}} - a_{1}\\
\vdots\\
\hat{a}_{N_G} - a_{N_{G}}\\
\end{bmatrix}=\begin{bmatrix}
\vec{\hat{b}}\\
\vec{\hat{a}}
\end{bmatrix}-\begin{bmatrix}
\vec{b}\\
\vec{a}
\end{bmatrix}
\end{equation}

A typical hybrid system, with a continuous plant and a discrete controller, is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$ 
\red{[this Delta term now refers to the continuous plant? this is not what has been discussed before, nor what is in some of the plots.]} 
, $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.

@@

\paragraph{The {\sc Synthesise} and {\sc Verify} phases}
The {\sc synthesise} phase uses a BMC-based verifier to 
compute a solution ($N_c$,$D_C$). An important remark is that this 
controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
domain.
A second remark is that the synthesis and verification engines use fixed/floating point arithmetic,
therefore we also need to examine the effect of discretization during these operations.
\cdsay{integrate the following with Dario}
Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
using Fixed-Point bit vectors with integer size $I_b$ and fractional
size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
%
\begin{align}
\small
\label{digital_controller_plant_tf}
\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
\end{align}

@@

%$$
%\begin{array}{ll}
%N_C(z) {=} 0z^2{+}0z{+}0\\
%D_C(z) {=} 0z^2{+}0z{+}0\\
%\end{array}
%$$
$$
\blue{
C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}
}
$$

In the first {\sc verify} phase we obtain the following counterexample:

$$
\blue{
\Delta{\vec{p}} = [0.026506~ 1.000610~ 1.002838]^T
}
$$

%$$
%\begin{array}{ll}
%\Delta N_G(z) = 0.026506\\
%\Delta D_G(z) = 1.000610z+1.002838
%\end{array}
%$$

We add this counterexample to {\sc inputs} and initiate the {\sc synthesise} phase, where we get the following candidate solution: 
%\red{[ How is the order of the candidate solution chosen here?]}
$$
\blue{
C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}
}
$$

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and the verifier signals
that it is due to lack of precision. We thus increase our precision to
$I_b=20,F_b=28$.
%
We stay in the {\sc verify} phase and receive a new counterexample at
higher precision:
\cdsay{Pascal, this sounds confusing. if you want to increase precision on-the-fly, i.e. 
not going back to the synthesise phase, 
then this illustration doesn't follow the general diagram in Fig.5. 
We need to decide which direction we keep.}
%
%$$
%\begin{array}{ll}
%\Delta N_G(z) {=} 0.026314\\
%\Delta D_G(z) {=} 0.999024z{-}1.004785
%\end{array}
%$$
$$
\blue{
\Delta{\vec{p}} = [0.026314~ 0.999024~ {-}1.004785]^T
}
$$

%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
Since previous counterexamples were attained at lower precision, we 
remove them from the counterexample set. In the next {\sc synthesise}
phase, we get a new candidate solution that holds for the newly
inserted counterexample:

$$
\blue{
C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}
}
$$
%
%$$
%\begin{array}{ll}
%N_C(z) {=} \\
%D_C(z) {=} \\
%\end{array}
%$$

@@

\blue{
For the same cruise control system, the synthesis may be done considering that the plant model have parametric uncertainties ($\Delta G_{P}(z)$). Thus, the synthesised controller must to stabilize for any parametric variation $\Delta p$ inside of a given region. Specially, in this example, was assumed that each coefficient of $G(z)$ may vary $\pm 0.5\%$.
}

\blue{Initially, the controller denominator and numerator  ($D_{C}(z)$ and $N_{C}(z)$) are started with zero coefficients, as in previous example. Thus,  in the first {\sc verify} phase a counterexample is presented, that is added to {\sc inputs}, whis is usede in the first  {\sc synthesise} phase. The resulting controller is:
}
$$
{
\blue{
C(z)=\frac{0.77516z^2{+}-0.71497z{+}0.03729}{0.25024z^2{-}0.01799z{+}0.00097}
}}
$$

\blue{In the second {\sc verify} phase, the controller failed to stabilize the system for all the range of uncertainties, another counterexample was provided, and the following candidate controller is presented in another {\sc synthesise} phase:}
$$
{
\blue{
C(z)=\frac{0.68970z^2{+}0.36538z{+}0.30637}{0.06862z^2{+}0.00394z{+}0.00802}
}}
$$

\blue{
This candidate solution is validated as the final solution by the next 
{\sc verify} phase.
}

@@

%---------------------------------
\subsection{Results}
\label{experimental-results}

\textcolor{red}{How did you obtain the results from Table~\ref{tab:results}? 
Can you provide the command-line? The reviewers should be able to reproduce our experiments.}
We outline the runtimes required to synthesise a stable controller for each
benchmark in Table~\ref{tab:results}. \textcolor{red}{Which section do you refer??
For most benchmarks the conjecture explained in section~\ref{fixedpoint_verification} 
holds and the inductive back-end is able to find a stable solution in less than one minute}. 
This is possible if the inductive solutions need to be refined with few counterexamples 
and fixed point precision increases. However, some of our benchmarks did not meet these criteria. 
\textcolor{red}{Which cases? Can you refer to Table~\ref{tab:results} In these cases, 
the interval arithmetic back-end is able to complement the inductive approach
and synthesise a solution instead, albeit with significantly larger runtimes}.

\textcolor{red}{Can you relate the benchmarks in Table~\ref{tab:results} in terms of 
$C$ and $G$ as described in section~\ref{experimental-setup}. You could add an additional column to that table.}

@@

\caption{Experimental results. \textcolor{red}{It should be a table and not a figure.} \label{tab:results}}
\end{figure}
%---------------------------------

\textcolor{red}{Can you provide the synthesised controllers? Iury could then check the solution using the bode diagram.}
We conclude from these results that the inductive back-end provides excellent performance
for synthesising stable controllers in the majority of the benchmarks \textcolor{red}{can you be more specific? which benchmarks?}, and can be
complemented using the interval arithmetic back-end, where the inductive conjectures fail
too frequently. Both back-ends enabled controller synthesis for all benchmarks within
reasonable time frames.

@@

In this study, we have investigated a CEGIS-based approach that uses inductive synthesis 
in conjunction with a robust closed-loop stability verification algorithm to find a parametric 
solution for a digital controller given a continuous (or discrete) plant specification.
In particular, we have exploited the automatic synthesis of correct-by-construction 
digital controllers along with a model of their physical environment.
We have also modeled a digital equivalent of the physical plant by evaluating the 
effects of the quantisers (A/D and D/A converters) as time discretisation elements 
with quantisation noise. Experimental results show that the inductive back-end of our
CEGIS-based approach is able to synthesise stable controllers in most benchmarks and can be 
complemented using the interval arithmetic back-end, where the inductive conjectures fail. 
Both back-ends enabled controller synthesis for all benchmarks within reasonable time frames.
Further studies include the extension of this CEGIS-based approach for different classes of systems
({\it e.g.}, state-space) and also consider performance requirements while synthesising 
the digital controller.

>>>>

The digital controllers synthesized in this paper are typically used in closed loops with continuous (and physical) plants. Thus, the proposed approach have to consider dynamics of continuous parts of system ({\it e.g.}, plant) and discrete parts ({\it e.g.}, digital controller), {\it i.e.} the synthesized controller have to consider the issues related to the hybrid systems studies.

@@

The vector of parametric uncertainties  $\Delta{p}$ for $G(z)$ is defined by:
\begin{equation}
\Delta{p}=\begin{bmatrix}
\hat{b_{0}} - b_{0}\\
\hat{b_{1}} - b_{1}\\
\vdots \\
\hat{b}_{M_G} - b_{M_{G}}\\
\hat{a_{0}} - a_{0}\\
\hat{a_{1}} - a_{1}\\
\vdots\\
\hat{a}_{N_G} - a_{N_{G}}\\
\end{bmatrix}=\begin{bmatrix}
\vec{\hat{b}}\\
\vec{\hat{a}}
\end{bmatrix}-\begin{bmatrix}
\vec{b}\\
\vec{a}
\end{bmatrix}
\end{equation}

\red{[where is this new variable used later?]}

A typical hybrid system \red{[clarify the adjective ``hybrid'']} is shown in Figure~\ref{fig:sampledsystem}, where the DAC and ADC converters introduce quantisation noises $\nu_{1}(z)$ and $\nu_{2}(z)$, $G(s)$ is the continuous-time plant model with parametric additive uncertainty $\Delta G_{P}(s)$ 
\red{[this Delta term now refers to the continuous plant? this is not what has been discussed before, nor what is in some of the plots.]} 
, $R(z)$ is the reference signal, $U(z)$ is the control signal, and $\hat{Y}(z)$ is the output signal affected by the noises and uncertainties in the closed-loop system.

@@

\paragraph{The {\sc Synthesise} and {\sc Verify} phases}
The {\sc synthesise} phase uses a BMC-based verifier to 
compute a solution ($N_c$,$D_C$). An important remark is that this 
controller is synthesised in the $\mathbb{R}\langle I,F \rangle$
domain.  
\cdsay{integrate the following with Dario}
Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
using Fixed-Point bit vectors with integer size $I_b$ and fractional
size $F_b$, whose domain is $\mathbb{R}\langle I_b,F_b \rangle \supseteq \mathbb{R}\langle I,F \rangle$.
%
\begin{align}
\small
\label{digital_controller_plant_tf}
\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
\end{align}

@@

$$
\begin{array}{ll}
N_C(z) {=} 0z^2{+}0z{+}0\\
D_C(z) {=} 0z^2{+}0z{+}0\\
\end{array}
$$

In the first {\sc verify} phase we obtain the following counterexample:
$$
\begin{array}{ll}
\Delta N_G(z) = 0.026506\\
\Delta D_G(z) = 1.000610z+1.002838
\end{array}
$$

We add this counterexample to {\sc inputs} and initiate the {\sc synthesise} phase, where we get the following candidate solution: 
%\red{[ How is the order of the candidate solution chosen here?]}
$$
\begin{array}{ll}
N_C(z) {=} 12.402664z^2{-}11.439667z{+}0.596756\\
D_C(z) {=} 4.003906z^2{-}0.287949z{+}0.015625\\
\end{array}
$$

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and the verifier signals
that it is due to lack of precision. We thus increase our precision to
$I_b=20,F_b=28$.
%
We stay in the {\sc verify} phase and receive a new counterexample at
higher precision:
\cdsay{Pascal, this sounds confusing. if you want to increase precision on-the-fly, i.e. 
not going back to the synthesise phase, 
then this illustration doesn't follow the general diagram in Fig.5. 
We need to decide which direction we keep.}
%
$$
\begin{array}{ll}
\Delta N_G(z) {=} 0.026314\\
\Delta D_G(z) {=} 0.999024z{-}1.004785
\end{array}
$$
%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
Since previous counterexamples were attained at lower precision, we 
remove them from the counterexample set. In the next {\sc synthesise}
phase, we get a new candidate solution that holds for the newly
inserted counterexample:

$$
\begin{array}{ll}
N_C(z) {=} 11.035202z^2{+}5.846100z{+}4.901855\\
D_C(z) {=} 1.097901z^2{+}0.063110z{+}0.128357\\
\end{array}
$$

@@

@@

%---------------------------------
\subsection{Results}
\label{experimental-results}
We outline the runtimes required to synthesise a stable controller for each
benchmark in Table~\ref{tab:results}. For most benchmarks the conjecture explained
in section~\ref{fixedpoint_verification} holds and the inductive back-end is able
to find a stable solution in less than one minute. This is possible if the inductive
solutions need to be refined with few counterexamples and fixed point precision
increases. However, some of our benchmarks did not meet these criteria. In these
cases the interval arithmetic back-end was able to complement the inductive approach
and synthesise a solution instead, albeit with significantly larger runtimes.

@@

\caption{Experimental results. \label{tab:results}}
\end{figure}
%---------------------------------

We conclude from these results that the inductive back-end provides excellent performance
for synthesising stable controllers in the majority of the benchmarks, and can be
complemented using the interval arithmetic back-end where the inductive conjectures fail
too frequently. Both back-ends enabled controller synthesis for all benchmarks within
reasonable time frames.

@@
